### 2016-11-09 README.Rmd
add vis_miss_ly
still under development, but a start
rename chunks and fix plots/figures in README

There are currently three main commands: `vis_dat`, `vis_miss`, and `vis_guess`

- `vis_dat` visualises a dataframe showing you what the classes of the columns are, and also displaying the missing data.

- `vis_miss` visualises just the missing data, and allows for missingness to be clustered and columns rearranged. `vis_miss` is similar to `missing.pattern.plot` from the `mi` package. Unfortunately `missing.pattern.plot` is no longer in the `mi` package (well, as of 14/02/2016).

-  `vis_guess` has a guess at what the value of each cell. So "10.1" will return "double", and `10.1` will return "double", and `01/01/01` will return "date". Keep in mind that it is a **guess** at what each cell is, so you can't trust this fully. `vis_guess` is made possible thanks to Hadley Wickham's `readr` package - thanks mate!

@@

@@

## Using `vis_dat`

@@

```{r vis_dat}

@@

```{r}

@@

```{r}

@@

```{r}

@@

## using `vis_miss`

We can explore the missing data further using `vis_miss`

```{r vis_miss}

@@

```{r vis_miss-cluster}

@@

```{r}

@@

```{r}

@@

```{r}

@@

## using `vis_compare`

Sometimes you want to see what has changed in your data. `vis_compare` helps with that. It is currently only just barely working, so keep in mind that this is very much in its beta stages.

@@

```{r}

@@

```{r}

@@

# vis_compare(iris, iris_diff_2)

@@

## using `vis_guess`

`vis_guess` takes a guess at what each cell is. It's best illustrated using some messy data, which we'll make here.

```{r}

messy_df <- data.frame(var1 = messy_vector,
                       var2 = sample(messy_vector),
                       var3 = sample(messy_vector))

```{r}

@@

```{r}

@@

>>>>

@@

There are two main commands in the `visdat` package: 
- `vis_dat()` 
- `vis_miss()`

- `vis_dat()` visualises a dataframe showing you what the classes of the columns are, and also displaying the missing data.

- `vis_miss()` visualises just the missing data, and allows for missingness to be clustered and columns rearranged. `vis_miss()` is similar to `missing.pattern.plot` from the `mi` package. Unfortunately `missing.pattern.plot` is no longer in the `mi` package (well, as of 14/02/2016).

There are two some experimental functions:

- `vis_guess()`
- `vis_compare()`

-  `vis_guess()` has a guess at what the value of each cell, using `readr::parse_guess`. This means that "10.1" will return "double", and `10.1` will return "double", and `01/01/01` will return "date". Keep in mind that it is a **guess** at what each cell is, so you can't trust this fully.

- `vis_compare()` compares two dataframes, displaying the differences.

@@

## Using `vis_dat()`

@@

```{r vis-dat-aq}

@@

```{r vis-dat-aq-sort-type}

@@

```{r vis-dat-typical-data}

@@

```{r vis-dat-typical-larger-data}

@@

## using `vis_miss()`

We can explore the missing data further using `vis_miss()`

```{r vis-miss-aq}

@@

```{r vis-miss-aq-cluster}

@@

```{r vis-miss-aq-sort-miss}

@@

```{r vis-miss-test}

@@

```{r vis-miss-mtcars}

@@

## Experimental features

## using `vis_compare()`

Sometimes you want to see what has changed in your data. `vis_compare()` helps with that. It is currently only just barely working, so keep in mind that this is very much in its beta stages.

@@

```{r vis-compare-iris}

@@

```{r vis-compare-error, eval = FALSE}

@@

vis_compare(iris, iris_diff_2)
#> vis_compare is still in BETA! If you have suggestions or errors, post an issue at https://github.com/njtierney/visdat/issuesthe condition has length > 1 and only the first element will be usedError: `.x` (5) and `.y` (6) are different lengths
```

## using `vis_guess()`

`vis_guess()` takes a guess at what each cell is. It's best illustrated using some messy data, which we'll make here.

```{r create-messy-vec}

set.seed(1114)
messy_df <- data.frame(var1 = messy_vector,
                       var2 = sample(messy_vector),
                       var3 = sample(messy_vector))

@@

```{r vis-guess-messy-df}

@@

```{r visdat-messy-df}

@@

## vis_dat_ly

This is still under development, but it is basically a faster version of doing a ggplot and then calling ggplotly.

## vis_miss_ly

This is also just brand new under development, but should prove interesting once I fix up the legend, etc.

```{r eval = FALSE, echo = TRUE}

vis_miss_ly(airquality)
